### 2015-03-15 Docs/managing_jobs/managingjobs.tex
more about yt

The scripts {\tt process-titan.run} and {\tt parallel-yt-new} in
{\tt MAESTRO/Util/job\_scripts/titan/} will manage the yt jobs
by calling a python script for each file that matches a pattern.

@@

{\em Note: this information may be out-of-date.}

>>>>

The scripts {\tt vis-titan.run} and {\tt parallel-yt-new} in {\tt
MAESTRO/Util/job\_scripts/titan/} will manage the yt jobs by calling a
python script for each file that matches a pattern.  Make sure you set
the proper path for the \yt\ {\tt activate} script in {\tt
parallel-yt-new}---this ensures that the paths to the various libraries
are set on the compute nodes.

Note that the actual visualization command itself is launched by
{\tt parallel-yt-new} using the {\tt aprun} command.

@@

{\em Note: this information may be out-of-date.  It is recommended that
 \yt\ be used instead.}
